Pythran: Bringing OpenMP to a Python Subset

### 2013-02-07 doc/papers/europar2013/paper.tex
Update nebchmark result thanks to Big's machine.

The Hyantes programs scales relatively well. Figure~\ref{fig:hyantes-speedup} shows
the relative speedup of the application when increasing the number of OpenMP
threads.

@@

The performance of the two approaches is shown in
Figure~\ref{fig:cython-pythran}.  The benchmarked codes are typical
mathematical, image-processing or linear algebra kernels. All these kernels have
been written in Cython and Python ---compatible with Pythran--- and annotated
through the mechanism of each language to exhibit parallelism, then compiled
into native code using GCC 4.7.2 and the \texttt{-O2 -fopenmp} flag. Their
execution time when called from the Python interpreter is measured through the
\texttt{timeit} module on a laptop with 4 Intel i7 cores at 2.10 GHz with
hyperthreading deactivated. All results are normalized against Cython sequential
execution time. They show that while being of a higher level than Cython,
Pythran achieves comparable results.

>>>>

The Hyantes programs scales relatively well. Figure~\ref{fig:hyantes-speedup} shows
the relative speedup of the application when increasing the number of OpenMP
threads using up to 8 AMD Opteron 6176 SE.

@@

The performance of the two approaches is shown in
Figure~\ref{fig:cython-pythran}.  The benchmarked codes are typical
mathematical, image-processing or linear algebra kernels. All these kernels
have been written in Cython and Python ---compatible with Pythran--- and
annotated through the mechanism of each language to exhibit parallelism, then
compiled into native code using GCC 4.7.2 and the \texttt{-O2 -fopenmp} flag.
Their execution time when called from the Python interpreter is measured
through the \texttt{timeit} module on a machine using 4 AMD Opteron 6176 SE.
All results are normalized against Cython sequential execution time. They show
that while being of a higher level than Cython, Pythran achieves comparable
results.
